\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/background.tex
minor fix

One of the key challenges for refraction networking is in taking over a session. The station must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client. A simple approach is to have the refraction station act as an inline transparent proxy (\cref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site. After a TLS handshake has been completed, the station terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.

@@

TapDance~\cite{tapdance14} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (\cref{fig:tapdance}). In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the station takes over the connection in its place. After a client would receive a packet initiated by the station, its TCP sequence numbers would become desynchronized with the decoy site, causing the decoy to ignore the packets sent by the client.

@@

\scheme is able to avoid these problems by creating proxies at unused IP addresses, allowing the station full control over a host it has created, rather than forcing it to mimic an already existing decoy (\cref{fig:dark-decoys}).
%The registration session is used to send a signal to the station to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference. The dark session connects to a dark address that is not routed to any host; the RS instead acts as a remote endpoint for the entirety of the connection, starting with the TCP handshake. 
This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in Section~\ref{sec:attacks}.

>>>>

One of the key challenges for refraction networking is in taking over a session. The station must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client. A simple approach is to have the refraction station act as an inline transparent proxy (Figure~\ref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site. After a TLS handshake has been completed, the station terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.

@@

TapDance~\cite{tapdance14} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (Figure~\ref{fig:tapdance}). In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the station takes over the connection in its place. After a client would receive a packet initiated by the station, its TCP sequence numbers would become desynchronized with the decoy site, causing the decoy to ignore the packets sent by the client.

@@

\scheme is able to avoid these problems by creating proxies at unused IP addresses, allowing the station full control over a host it has created, rather than forcing it to mimic an already existing decoy (Figure~\ref{fig:dark-decoys}).
%The registration session is used to send a signal to the station to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference. The dark session connects to a dark address that is not routed to any host; the RS instead acts as a remote endpoint for the entirety of the connection, starting with the TCP handshake. 
This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in Section~\ref{sec:attacks}.
